
\newglossaryentry{XamarinForms}
{
  name=Xamarin Forms,
  description={is a framework developed by Xamarin Inc in \printdate{28.5.2014} to rappidly built crossplatfrom apps. It can be compiled to iOS, Android an Windows Phone from a shared code base}
}

\newglossaryentry{scrum}
{
  name=Scrum,
  description={is a management and control process that cuts through complexity to focus on building software that meets business needs. Management and teams are able to get their hands around the requirements and technologies, never let go, and deliver working software, incrementally and empirically\cite{scru16}}
}

\newglossaryentry{AgileSoftwareDevelopment}
{
  name=Agile Software Development,
  description={refers to approaches in software development process, which should improve transparency and flexibility and result in a rapid onset of the developed systems, in order to minimize risks in the development process. The core idea is to keep the sub-processes as simple and thus moveable (= agile)\cite{SiMaV5}}
}

\newglossaryentry{XamarinStudio}
{
  name=Xamarin Studio,
  description={, a standalone IDE for mobile app development, was released in February 2013 as part of Xamarin 2.0 and is based on the open source project MonoDevelop. In addition to a debugger, Xamarin Studio includes code completion in C\#, an Android UI builder for creating user interfaces without XML, and integration with Xcode Interface Builder for iOS app design}
}

\newglossaryentry{nuget}
{
  name=Nuget,
  description={is open source package manager for .Net projects developed by microsoft
  \href{http://nuget.codeplex.com/}{Homepage}}
}

\newglossaryentry{overlay}
{
  name=overlay,
  description={is an way to display additonal data on top of some thing else like a map. Can be a image or a shape or something else}
}

\newglossaryentry{renderer}
{
  name=renderer,
  description={component of Xamarin Forms, responsible to create the actual represenation for the data for the device}
}

\newglossaryentry{polygon}
{
  name=polygon,
  description={is a plane figure that is bounded by a finite chain of straight line segments closing in a loop to form a closed chain or circuit}
}

\newglossaryentry{Geofencing}
{
	name=Geofencing,
	description={is a feature in a software program that uses the global positioning system (GPS) to define geographical boundaries. A geofence is a virtual barrier}
}

%%% Acronyms

\newdualentry{xml} % label
  {XML}            % abbreviation
  {Extensible Markup Language}  % long form
  {is a markup language to display hierarchic structured data in text files} % description

\newdualentry{kml} % label
  {KML}            % abbreviation
  {Keyhole Markup Language}  % long form
  {is a markup language based on XML used for geospatial data} % description
  
\newdualentry{api} % label
	{API}            % abbreviation
	{Application program interface}  % long form
	{is a software intermediary that makes it possible for application programs to interact with each other and share data. It's often an implementation of REST that exposes a specific software functionality while protecting the rest of the application} % description
  
\newdualentry{ide} % label
	{IDE}            % abbreviation
	{Integrated development environment}  % long form
	{is a software application that provides comprehensive facilities to computer programmers for software development. An IDE normally consists of a source code editor, build automation tools and a debugger. Most modern IDEs have an intelligent code completion} % description

\newdualentry{sofa} % label
	{SOFA}            % abbreviation
	{Software Factory}  % long form
	{is the last project type module in the curriculum. To make it as real life as possible, a real customer is involved. The students work in groups, each group having its own customer and is using product specific technologies\cite{FoSE14}} % description