\section{Reflection}
\subsection{Max van der Linden}
As the project leader of the SoFa TreeWatch group I learned a lot about what it means to lead a project. This meant that i had to make sure that everyone follows the rules and sticks to the deadlines. One of the tasks of the project leader was also to be the main contacting point to and from the customer. From this i learned a lot about communicating in a professional way.

All in all in my opinion a good and useful product form which a lot was learned.

\subsection{Martijn Bonajo}

I learned a lot from this project. For me it was the first time creating a multi platform application. This meant learning how to work with Xamarin, using MVVM on the \gls{XamarinForms} and programming to platform specific \gls{api}s.\\
As configuration manager I was responsible for making sure everyone could run all the software that was needed during the project.

\subsection{Rene Karoff}
During this project my role was the project quality manager. This means that my responsibility was to define the quality standards and to make sure that the defined standards were met during the project. This went well most of the time, but since I study Business Informatics I am not as experienced in coding as the Software Engineering students, I wasn't always able to push the group to the test-driven way of developing the features. As the project quality manager i put myself in the role of reviewing every document and implemented user story. During the next project I would define that rule different, as that the reviewer switches. This should lead to a higher quality since more eyes will see more errors.

All in all my quality management skills really improved during this project and I was also able to contribute code to the project which improved my coding skills too.

The experience of working for a real customer was really nice, especially because we had a customer where it was pleasant to work with. The customer was able to define his needs in a understandable way and because of that I also learned something about precision farming.
\subsection{Jan Kerkenhoff}
I learned a lot about cross platform development and also about C\# development. It was my first time developing a mobile app and also never did work on anything cross platform. I gained a lot of knowledge about Xamarin and \gls{XamarinForms}.
As the main developer is was responsible for solving all programming related challenges, pick out the frameworks and libraries we used and helping others out if they were stuck. Also kept an eye on the Test Driven Development process together with René. This thought me a lot about writing tests and challenges when doing TDD.


\subsection{Ron Gebauer}

In this project I learn a bunch of stuff. As an example I worked the first time with \gls{XamarinStudio} and was a part in the creation of an cross platform application. Furthermore I learned a lot from our customer, which creates an really interesting atmosphere inside the meetings. In addition to that I got more and more confirm with \gls{scrum}, which was our \gls{AgileSoftwareDevelopment} method.		
		
Finally I will say that this \gls{sofa} one of the most interesting and helping modules was in my study.
