\section{Project analysis and prioritization}
\label{analysis}
Content of this chapter is all that happens in the beginning of the project. What contains all talks between us and the company for which the project is. Furthermore, out thinking about the project in the beginning, the analysis of what the user wants to get at the end and final the mockup planning of the menu structure.

\subsection{Planning and the desired results of the analysis phase}
The analysis phase started on 31-08-2015 and proceeded over a period of 2 milestones that were each 2 weeks long. The end of the stage was therefore the 25-09-2015.

\paragraph{In the first milestone} the requirements of the application were examined. From the results various Epics and User Stories have been created, which have been prioritised by our contact person in Fleuren Baarlo and accordingly brought into order.

\paragraph{The second milestone} was launched with finding ways of development and the currently used systems. After the systems were determined, various guidelines had to be created to determine how to be developed.
Following mock-ups are created to represent the structure of the surface.

\subsection{Results and their discussion within the Milestones}
The results of the first milestone are in Table~\ref{tab:RequirementsAndUserStories} of the \ref{sec:Requirements}.~Section. While the results of the second milestone, which have been expanded in the design phase, can be found in Section~\ref{sec:Design}.

At the beginning of the project a discussion with Yannick Smedts took place, our future contact person within Fleuren Baarlo, about their wishes to the application being created.

During the next few days some questions arose that were answered and discussed during a further meeting, what was extended with a visit to Van Den Borne aardappelen.

Finally, a last talk was organised in Fleuren Baarlo to clarify the recent ambiguities and thus successfully complete the analysis phase.

\paragraph{The talks took place as follows:}
\begin{itemize}
	\item 31-08-2015 \href{http://fontys.nl}{Fontys University of Applied Science Venlo}
	\item 09-09-2015 \href{http://fleuren.net}{Fleuren Baarlo} headquarter and on a field
	\item 17-09-2015 \href{http://www.vandenborneaardappelen.com}{Van Den Borne aardappelen}
	\item 25-09-2015 \href{http://fleuren.net}{Fleuren Baarlo} headquarter
\end{itemize}
