\section{Planning}
This chapter is about the overall planning of the TreeWatch project, which means it contains the roles each group member was elected for. Furthermore the overall planning contains the different project phases, the deliverables and milestones as well as the time-planning.
\subsection{Roles}
The following rules were assigned to the group members by the group. Every groupmember was asked to give his preferred role and since there were nor conflicts everyone got the role which he peferred. Each role had it's own responsibilities which are described in this subchapter.
\begin{description}
	\item[Project Manager] \hfill \\
	This role was given to Max van der Linden as he studies Business Informatics which is a good basis for this role. Teh project manager was responsible for the communication with the customer and the planning of the project.
	\item[Quality Manager] \hfill \\
	The Quality Manager  role was assigned to René Karoff. The Quality Manager was responsible for defining the quality standards which have to be met by all implemented features e.g. code-coverage in testing or coding styleguides. Furthermore he took care of the requirements and that everything implemented matched them. 
	\item[Scrum Master] \hfill \\
	The Scrum Master role was chosen by Ron Gebauer. The Scrum Master was had the task to set up the scrum environment and to solve problems. This means that, if there were problems which kept the group or a group member from working on the project he was about to solve it. 
	\item[Configuration Manager] \hfill \\
	The Configuration Manager had to make sure that the development environment ran smooth. This means e.g. solve issues with the used IDE or used servers.
	\item[Main Software Engineer] \hfill \\
	The Main Software Engineer was responsible for the implementation. He made sure that coding was done. If someone struggled with an issue too long, he tried to help him out.\ldots
\end{description}