\section{Reflection}
\subsection{Max van der Linden}
As the project leader of the SoFa TreeWatch group I learned a lot about what it means to lead a project. This meant that I had to make sure that everyone follows the rules and sticks to the deadlines. One of the tasks of the project leader was also to be the main contacting point to and from the customer. From this I learned a lot about communicating in a professional way.

All in all, in my opinion a good and useful product form which a lot was learned.

\subsection{Martijn Bonajo}

I learned a lot from this project. For me it was the first time creating a multi platform application. This meant learning how to work with Xamarin, using MVVM on the \gls{XamarinForms} and programming to platform specific \gls{api}s.\\
As configuration manager I was responsible for making sure everyone could run all the software that was needed during the project.

\subsection{Rene Karoff}


\subsection{Jan Kerkenhoff}


\subsection{Ron Gebauer}
In this project I learn a bunch of stuff. As an example I worked the first time with \gls{XamarinStudio} and was a part in the creation of an cross platform application. Furthermore I learned a lot from our customer, which creates an really interesting atmosphere inside the meetings. In addition to that I got more and more confirm with \gls{scrum}, which was our \gls{AgileSoftwareDevelopment} method.

Finally I will say that this \gls{sofa} one of the most interesting and helping modules was in my study.