
\newglossaryentry{XamarinForms}
{
  name=Xamarin Forms,
  description={is a framework developed by Xamarin Inc to rappidly built crossplatfrom apps. It can be compiled to iOS, Android an Windows Phone from a shared code base.}
}

\newglossaryentry{nuget}
{
  name=Nuget,
  description={is open source package manager for .Net projects developed by microsoft
  \href{http://nuget.codeplex.com/}{Homepage} }
}

\newglossaryentry{overlay}
{
  name=overlay,
  description={is an way to display additonal data on top of some thing else like a map. Can be a image or a shape or something else.}
}

\newglossaryentry{renderer}
{
  name=renderer,
  description={component of Xamarin Forms, responsible to create the actual represenation for the data for the device}
}

\newglossaryentry{polygon}
{
  name=polygon,
  description={is a plane figure that is bounded by a finite chain of straight line segments closing in a loop to form a closed chain or circuit}
}

\newglossaryentry{Geofencing}
{
	name=Geofencing,
	description={is a feature in a software program that uses the global positioning system (GPS) to define geographical boundaries. A geofence is a virtual barrier.}
}

\newglossaryentry{maptiles}
{
  name=map tiles,
  description={is part of a way maps are displayed digitally, each tile corresponds to a specific area of the map. Ever map consists of multiple tiles that contain information for ever zoom level}
}

%%% Acronyms

\newacronym{app}{app}{Application}

\newdualentry{gui} % label
  {GUI}            % abbreviation
  {Graphical User Interface}  % long form
  {is a user interface that includes graphical elements, such as windows, icons and buttons} % description

\newdualentry{xml} % label
  {XML}            % abbreviation
  {Extensible Markup Language}  % long form
  {is a markup language to display hierarchic structured data in text files} % description

\newdualentry{kml} % label
  {KML}            % abbreviation
  {Keyhole Markup Language}  % long form
  {is a markup language based on XML used for geospatial data} % description

\newdualentry{api} % label
	{API}            % abbreviation
	{Application program interface}  % long form
	{is a software intermediary that makes it possible for application programs to interact with each other and share data. It's often an implementation of REST that exposes a specific software functionality while protecting the rest of the application.} % description
