\section{User Stories}
	\renewcommand{\arraystretch}{2.6}
	\begin{longtable}{ l l l r r }
		\multicolumn{3}{p{8.5cm}}{\textbf{Name}} & \textbf{Entity State} & \textbf{Business Value} \\
		\hline
		\multicolumn{3}{p{8.5cm}}{As a user, I want to correlate the available data in different views so that I can see the relations between different datasets.} & Open & Nice To Have \\
		\multicolumn{3}{p{8.5cm}}{As a user, I want the application to contain different forms to transmit different information about the actual state of the trees on the field (e.g. brown leaves, thin stems...).	} & Open & Nice To Have \\		\multicolumn{3}{p{8.5cm}}{As a user, I want to digitize the kwekerij schrift (Nursery Script)} & Open & Nice To Have \\		\multicolumn{3}{p{8.5cm}}{As a user, I want the application to analyze the data of the trees and give hints and solutions for problems.} & Open & Nice To Have \\		\multicolumn{3}{p{8.5cm}}{As a user, I want the application to register as much data as possible, automatically.} & Open & Nice To Have \\		\multicolumn{3}{p{8.5cm}}{As a user, I want to have a system that manages my customers, their orders and the amount of trees that are growing or are fully grown for them.} & Open & Nice To Have \\		\multicolumn{3}{p{8.5cm}}{As a user, I want to have an application on my portable devices so that it is possible for me to check all information everywhere.} & In Progress & Great \\		\multicolumn{3}{p{8.5cm}}{\textbf{Name}} & \textbf{Entity State} & \textbf{Business Value} \\
		\hline
		 & \multicolumn{2}{l}{Data entry} & In Progress & Great \\		 &  & \parbox{7.5cm}{As a user, I want my GPS data entered into the system.} & Open & Great \\		 &  & \parbox{7.5cm}{As a user, I want my weather data entered into the system.} & Open & Good \\		 &  & \parbox{7.5cm}{As a user, I want my soil data gathered into the system.} & Open & Nice To Have \\		 &  & \parbox{7.5cm}{As a user, I want my stem data entered into the system.} & Open & Nice To Have \\		 &  & \parbox{7.5cm}{As a user, I want the ability to fill out forms within the application.} & Open & Good \\		 &  & \parbox{7.5cm}{As a user, I want to be able to take pictures of the trees.} & In Progress & Good \\		 & \multicolumn{2}{l}{Logging} & Open & Great \\		 &  & \parbox{7.5cm}{As a user, I want to be able to specify what work I am doing on a field/block/row/tree.} & Open & Great \\		 & \multicolumn{2}{l}{Main functionality} & In Progress & Must Have \\		 &  & \parbox{7.5cm}{As a user, I want to have my field represented graphically in the application.} & Done & Must Have \\		 &  & \parbox{7.5cm}{As a user, I want to be able to see a chronological ordering of events that happened on trees in a certain row/block’s history.} & Open & Good \\		 &  & \parbox{7.5cm}{As a user, I want to be able to see where and how long I worked on a field.} & Open & Great \\
		\multicolumn{3}{p{8.5cm}}{\textbf{Name}} & \textbf{Entity State} & \textbf{Business Value} \\
		\hline
		 &  & \parbox{7.5cm}{As a user, I want to have overlays for my fields that show collected data.} & Open & Must Have \\		 &  & \parbox{7.5cm}{As a user, I want to get my data from a data storage where everything is inside.} & Done & Must Have \\		 &  & \parbox{7.5cm}{As a user, I want to have a lot of GPS functionality inside the map.} & Open & Nice To Have \\		 &  & \parbox{7.5cm}{As a user, I want to be able to overlay the field with various data.} & Open & Nice To Have \\		 &  & \parbox{7.5cm}{As a user, I want to be able to filter and search inside the blocks of a field.} & Done & Nice To Have \\
		\caption{User Stories\label{tab:userStories}}
	\end{longtable}